\Title

### 2019-06-11 manuscript/manuscript.tex
Format a version for the EarthArxiv (#63)
Use the Latex article class instead of GJI and insert the self-archiving
text from the publisher.
Add citation information for version of record and its DOI.
Add DOI link and citation to README.
Better formatting for citation in README.

\newcommand{\Title}{
    Gravitational field calculation in spherical coordinates using variable
    densities in depth
}
\newcommand{\Author}{S.R. Soler, A. Pesce, M.E. Gimenez, L. Uieda}
\newcommand{\AuthorAffil}{
    {\large
        Santiago R. Soler$^{1,2,*}$, Agustina Pesce$^{1,2}$,
        Mario E. Gimenez$^{1,2}$, and Leonardo Uieda$^3$
    }
    \\[0.4cm]
    {\small $^1$ CONICET, Argentina}
    \\
    {\small $^2$ Instituto Geofísico Sismológico Volponi, Universidad Nacional de San Juan, Argentina}
    \\
    {\small $^3$ Department of Earth Sciences, SOEST, University of Hawai'i at M\={a}noa, USA}
    \\
    {\small $^*$ e-mail: santiago.r.soler@gmail.com}
}

\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[round]{natbib}
\usepackage{fixltx2e}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\hypersetup{
    allcolors=blue,
    pdftitle={\Title},
    pdfauthor={\Author},
}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{
    \fontsize{9pt}{12pt}\selectfont
    \Author (2019).
    Accepted for publication in \textit{Geophysical Journal International}.
}
\rhead{\fontsize{9pt}{12pt}\selectfont \thepage}
\renewcommand{\headrulewidth}{0pt}

@@

\title{\Title}
\author{\AuthorAffil}
\date{
    \normalsize
    Accepted 2019 June 05. Received 2019 May 10; in original form 2018 December 29
    \\[0.4cm]
    This is a pre-copyedited, author-produced PDF of an article accepted for
    publication in \textit{Geophysical Journal International} following peer review.
    The version of record
    ``\textit{INSERT COMPLETE CITATION INFORMATION HERE}''
    is available online at: \href{https://doi.org/XXXXXXX}{doi.org/XXXXXX}
}
\maketitle

>>>>

\newcommand{\Title}{
    Gravitational field calculation in spherical coordinates using variable
    densities in depth
}
\newcommand{\Author}{S.R. Soler, A. Pesce, M.E. Gimenez, L. Uieda}
\newcommand{\AuthorAffil}{
    {\large
        Santiago R. Soler$^{1,2,*}$, Agustina Pesce$^{1,2}$,
        Mario E. Gimenez$^{1,2}$, and Leonardo Uieda$^3$
    }
    \\[0.4cm]
    {\small $^1$ CONICET, Argentina}
    \\
    {\small $^2$ Instituto Geofísico Sismológico Volponi, Universidad Nacional de San Juan, Argentina}
    \\
    {\small $^3$ Department of Earth Sciences, SOEST, University of Hawai'i at M\={a}noa, USA}
    \\
    {\small $^*$ e-mail: santiago.r.soler@gmail.com}
}
\newcommand{\DOI}{doi:\href{https://doi.org/10.1093/gji/ggz277}{10.1093/gji/ggz277}}
\newcommand{\DOILink}{\href{https://doi.org/10.1093/gji/ggz277}{doi.org/10.1093/gji/ggz277}}

\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[round]{natbib}
\usepackage{fixltx2e}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\hypersetup{
    allcolors=blue,
    pdftitle={\Title},
    pdfauthor={\Author},
}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{
    \fontsize{9pt}{12pt}\selectfont
    \Author{}, 2019. \DOI{}
}
\rhead{\fontsize{9pt}{12pt}\selectfont \thepage}
\renewcommand{\headrulewidth}{0pt}

@@

\title{\Title}
\author{\AuthorAffil}
\date{
    \normalsize
    Accepted 2019 June 05. Received 2019 May 10; in original form 2018 December 29
    \\[0.4cm]
    This is a pre-copyedited, author-produced PDF of an article accepted for
    publication in \textit{Geophysical Journal International} following peer review.
    The version of record
    ``\textit{Soler, S. R., Pesce, A., Gimenez, M. E., \& Uieda, L., 2019.
    \Title{}, Geophysical Journal International, \DOI{}}\ ''
    is available online at: \DOILink{}
}
\maketitle
